Reducing iptables configuration complexity using chains

### 2014-04-21 iptables/presentation.tex
use a capital I at the beginning of a sentence
highlight added and removed rules
add 'Example' to title

    iptables is a tool for creating the rulesets for netfilter, a packet filtering framework which was introduced in the linux 2.4 kernel

@@

@@

      \sout{-A INPUT -j DROP}}

@@

    \frametitle{Firewall for your server}

@@

      -A OUTPUT -m tcp -p tcp --sport ssh -j ACCEPT\\

@@

      -A OUTPUT -m tcp -p tcp --sport https -j ACCEPT}

@@

      -A OUTPUT -m state --state ESTABLISHED,RELATED -j ACCEPT}

@@

      \sout{-A webmaster\_IP -j DROP}\\
      -A webmaster\_IP -j admin\_IP}

@@

      \small{\sout{-A INPUT -p tcp -m tcp --dport 445 -j admin\_IP}\\

@@

      \sout{-A INPUT -p tcp -m tcp --dport 139 -j admin\_IP}\\

>>>>

    Iptables is a tool for creating the rulesets for netfilter, a packet filtering framework which was introduced in the linux 2.4 kernel

@@

      \small{{\color{blue}-P INPUT DROP}\\

@@

      \sout{{\color{red}-A INPUT -j DROP}}}

@@

    \frametitle{Example : firewall for your server}

@@

      {\color{blue}-A OUTPUT -m tcp -p tcp --sport ssh -j ACCEPT\\

@@

      -A OUTPUT -m tcp -p tcp --sport https -j ACCEPT}}

@@

      {\color{blue}-A OUTPUT -m state --state ESTABLISHED,RELATED -j ACCEPT}}

@@

      \sout{{\color{red}-A webmaster\_IP -j DROP}}\\
      {\color{blue}-A webmaster\_IP -j admin\_IP}}

@@

      \small{\sout{{\color{red}-A INPUT -p tcp -m tcp --dport 445 -j admin\_IP}}\\

@@

      \sout{{\color{red}-A INPUT -p tcp -m tcp --dport 139 -j admin\_IP}}\\
